Parsing Postfix Log Files

### 2009-04-28 doc/logparser-complications.tex
A change to the abstract suggested by Carl. Switch to one-and-a-half spacing for the initial submission.

Occasionally, a log file will have out of order log lines that cannot be
dealt with by the techniques described in \sectionref{tracking re-injected
mail}, \sectionref{discarding cleanup log lines}, or \sectionref{pickup
logging after cleanup}.  In the \numberOFlogFILES{} log files used in
\sectionref{Evaluation} this problem occurs only five times in 60,721,709
log lines.  All five occurrences have the same characteristics: the
\daemon{local} log line showing delivery to a user's mailbox comes after
the \daemon{qmgr} log line showing removal of the mail from the queue
because delivery is complete.  This causes several problems: the data in
the state tables for the mail is not complete, so it cannot be entered into
the database; a new mail is created when the \daemon{local} log line is
processed and remains in the state tables; four warnings are issued per
pair of out of order log lines.

>>>>

Occasionally, a log file will have out of order log lines that cannot be
dealt with by the various techniques described in \sectionref{tracking
re-injected mail}, \sectionref{discarding cleanup log lines}, or
\sectionref{pickup logging after cleanup}.  In the \numberOFlogFILES{} log
files used in \sectionref{Evaluation} this problem occurs only five times
in 60,721,709 log lines.  All five occurrences have the same
characteristics: the \daemon{local} log line showing delivery to a user's
mailbox comes after the \daemon{qmgr} log line showing removal of the mail
from the queue because delivery is complete.  This causes several problems:
the data in the state tables for the mail is not complete, so it cannot be
entered into the database; a new mail is created when the \daemon{local}
log line is processed and remains in the state tables; four warnings are
issued per pair of out of order log lines.

### 2009-04-28 doc/logparser.tex
Changes based on proofreading chapters 4 and 5.
Corrections to chapter 6 from proofreading.
Changes made to chapter 6 after proofreading.
Changes made after proofreading chapter 7 and the appendices.
Changes made after final checks.
Laid out my own abstract so that I could reuse it for my loose abstract page.
A change to the abstract suggested by Carl. Switch to one-and-a-half spacing for the initial submission.

@@

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[3][ ]{%
    \url{#2}#1(last checked #3)%
}
\newcommand{\daemonDocURL}[3][]{%
    \hfill{} \newline{} \url{#2}%
    \hfill{} #1 Last checked #3%
}

@@

@@

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\acronym{PLP}}
\newcommand{\parsernames}{\acronym['s]{PLP}}
\newcommand{\parsernamelong}{Postfix Log Parser}
\newcommand{\parsernameshort}{PLP}

@@

@@

@@

\begin{flushright}
    \underline{\hspace*{10em}} \\~\\
    John Tobin \\
    \today{}
\end{flushright}

@@

\noindent{}I am grateful to my wife, Ariane Tobin, for her patience, good
will, and encouragement.

\begin{abstract}

    \setcounter{page}{4}
    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, the difficulties encountered and the solutions
    developed.  The parser stores data gleaned from the log files in an SQL
    database; the gathered data can be used to optimise current anti-spam
    measures, to produce statistics showing how effective those measures
    are, or to provide a baseline to test new anti-spam measures against.
    The Postfix log file parser needs to be very precise and strict when
    parsing, yet must allow users to easily adapt or extend it to parse new
    log lines, without requiring that the user have an in-depth knowledge
    and understanding of the parser's internal workings.  The newly
    developed architecture is designed to make the process of parsing new
    inputs as simple as possible, enabling users to trivially add new rules
    (to parse variants of known inputs) and relatively easily add new
    actions (to process a previously unknown category of inputs).  The
    parser implemented for this project is evaluated on the criteria of
    efficiency and coverage of Postfix log files, demonstrating that the
    conflicting goals of efficiency and accuracy can be balanced, and that
    one need not be sacrificed to achieve the other.

@@

\end{abstract}

>>>>

% College expect one and a half or double spacing for the initial
% submission.
\usepackage{setspace}
\onehalfspacing{}

@@

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[3][ ]{%
    \url{#2}#1(last checked #3)%
}
\newcommand{\daemonDocURL}[3][]{%
    \hfill{} \newline{} \url{#2}%
    \hfill{} \newline{} #1 Last checked #3%
}

@@

\newcommand{\numberOFlogFILESallYEARS}[0]{%
    2 years, 1\textonehalf{} months%
}

@@

\newcommand{\numberOFrulesMINUSten}[0]{%
    174%
}

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}[1][]{\acronym[#1]{PLP}}
\newcommand{\parsernames}[0]{\acronym['s]{PLP}}
\newcommand{\parsernamelong}[0]{Postfix Log Parser}
\newcommand{\parsernameshort}[1][]{PLP#1}

@@

\newcommand{\titleandauthor}[0]{%
\begin{center}

@@

\end{center}
}

\titleandauthor{}

@@

\begin{flushright}
    \underline{\hspace*{15em}} \\~\\
    John Tobin \\
    \today{}
\end{flushright}

@@

\noindent{}I am grateful to my wife, Ariane Tobin, for her patience, good
will, and encouragement; without her, I would not have accomplished this.

% Abstract
\specialpage{Abstract}

~\empty{}

\vfill{}
\vfill{}
\vfill{}

%\titleandauthor{}

\begin{center}
    \textbf{Abstract}
\end{center}

Parsing Postfix log files is much more difficult than it first appears, but
it \textit{is\/} possible to achieve a high degree of accuracy in
understanding Postfix log files, and subsequently in reconstructing the
actions taken by Postfix when processing mail delivery attempts.  This
thesis describes the creation of a parser for Postfix log files,
documenting the architecture developed for this project and the parser that
implements it, the difficulties encountered and the solutions developed.
The parser stores data gleaned from the log files in an SQL database;
future projects or programs could use the gathered data to optimise current
anti-spam measures, to produce statistics showing how effective those
measures are, or to provide a baseline to test new anti-spam measures
against.  The Postfix log file parser needs to be very precise and strict
when parsing, yet must allow users to easily adapt or extend it to parse
new log lines, without requiring that the user have an in-depth knowledge
and understanding of the parser's internal workings.  The newly developed
architecture is designed to make the process of parsing new inputs as
simple as possible, enabling users to trivially add new rules (to parse
variants of known inputs) and relatively easily add new actions (to process
a previously unknown category of inputs).  The parser implemented for this
project is evaluated on the criteria of efficiency and coverage of Postfix
log files, demonstrating that the conflicting goals of efficiency and
accuracy can be balanced, and that one need not be sacrificed to achieve
the other.

@@

\vfill{}
\vfill{}
\vfill{}

~\empty{}
